---
title: "GDP growth and investment"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(readstata13)
```

## Part 1: True False Questions
1, Endogeneity of regressors causes that the OLS coeffecients are biased.
True.
Because the estimated coeffecients are not BLUE anymore

2, Dropping an important variable from the set of regressors always creates an omitted variable bias.
False.
Omitted variable bias only happens when residuals correlated with explanatory variables.
If dropped variable doesn???t affect to other explanatory variables, the residuals into which the impact of the dropped variable entered does not also affect to other variables.

3, A high degree of correlation between the explanatory variables causes that the OLS coefficients are biased.
False.
Multicollinearity causes to increase of variance of OLS coefficients, but not causes to biasnesss.

4,
R^2 = Var(y^)/Var(y) = 7.8/10.3 = 0.75728???
R-squared close to 1. This means that the model explains the data well.

5, Including an irrelevant variables does not lead to biased OLS coefficients.
True.
It leads to multicollinearity which cause to increase of variance of OLS coefficients.

6, I reject a Null-hypothesis on a single coefficient, if the absolute value of the t-statistics is larger than the critical value.
True.

7, An OLS estimator becomes more accurate, the larger the dispersion of the explanatory variables x_it.
True.
If the Var(x_it) becomes larger, the Var(B^) will decrease.



## Part2: Regression preparetion

(a)
Firstly, We generate the variables that we need for running Cobb-Douglas production function.

#1 read CobbDouglas.dta
```{r}
cobbdata <- read.dta13("/Users/Takuma/Google Drive/GitHub/GDP-Growth-and-Investment/CobbDouglas.dta")
```

#2 generate explanatory variables
```{r}
class(cobbdata)
head(cobbdata)
logY <- log(cobbdata["gsp"])
logK1 <- log(cobbdata["hwy"] + cobbdata["water"] + cobbdata["util"])
logK2 <- log(cobbdata["pc"])
logL <- log(cobbdata["emp"])
unemp <- cobbdata["unemp"]
```

(b)
Because we have to avoid omitted variable biases.
If we omit these variables (private capital, employment rate), the residual may significantry correlated with explanatory variable (public capital). That leads to biasness of estimated coeficients.


##Estimating pooled OLS

(a)
```{r}

```
